On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-26 docs/mvfits_paper/mvf.tex
misc updates

\par Both Phenom and \eob{} approaches directly use phenomenological models (i.e. fits) for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations \cite{Leaver85}.

>>>>

\par Both Phenom and \eob{} approaches directly use phenomenological models for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations \cite{Leaver85}.
